Data_visualization

### 2018-09-07 Rmd/Data_visualization_common_names.Rmd
csv´s with total pollen on stigma (N=3)

---
title: "Data_visualization"
output:
      pdf_document
---
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
#Preparing seed set plots, starting with Petunia

>>>>

---
title: "Data_visualization"
output:
      pdf_document
---

###SEED SET PER SPECIES WITH DIFFERENT TREATMENTS
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
#Preparing seed set plots, starting with Petunia
